---
title: "peer1assignmentreproduciable"
author: "Prafull"
date: "July 27, 2018"
output: 
  html_document: 
    keep_md: yes
---

###Reading data 
```{r}
library(knitr)
library(ggplot2)
library(dplyr)
readdata <- read.csv("C:\\Users\\Mahe\\Desktop\\Data Science\\Reproducible-research\\project1\\activity.csv")
readdata1 <- readdata[!is.na(readdata$steps) ,]
head(readdata1)
```

###Histogram of the total number of steps taken each day
```{r }


readdata1$date <- as.Date(readdata1$date)
sum_steps <- readdata1 %>% group_by(date) %>% summarise(total_sum = sum(steps))
sum_steps



plot_1 <- hist(sum_steps$total_sum , col = "green" , xlab = "Total no of steps taken each day" , main = "Histogram of total no of steps taken each day")
plot_1
```

###Mean and median number of steps taken each day
```{r}
mean_of_step_taken = mean(readdata1$steps)
mean_of_step_taken
median_of_step_taken = median(readdata1$steps)
median_of_step_taken
```

###Time series plot of the average number of steps taken

```{r}
avg_steps = readdata1 %>% group_by(interval) %>% summarise(avg_steps = mean(steps))

plot(avg_steps$interval, avg_steps$avg_steps , type = "l" , xlab = "Intervals" , ylab = "average steps")


```

###The 5-minute interval that, on average, contains the maximum number of steps
```{r}
max_interval = avg_steps$interval[which.max(avg_steps$avg_steps)]
max_interval
```

### we use mean of interval to replace na value of a particular interval
```{r}

n <- nrow(readdata)

for(i in 1:n)
{
    
    if(is.na(readdata$steps[i])){
      c <- which(readdata$interval[i] == avg_steps$interval )
      readdata$steps[i] <- avg_steps[c,]$avg_steps
    }
}

head(readdata$steps)
```
###Histogram of the total number of steps taken each day after missing values are imputed
```{r}

sum_steps <- readdata1 %>% group_by(date) %>% summarise(total_sum = sum(steps))
hist(sum_steps$total_sum, 
     xlab="Total number of steps taken each day", 
     ylab="Count", 
     main="Histogram of total number of steps taken each day",
     col=3)
```

###Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
  library(lubridate)
  readdata$date <- as.Date(readdata$date)
  readdata2 <- readdata
  readdata2$daytype <- "Weekday"
  readdata2$day <- wday(readdata$date , label = T)
  
  for(i in 1:n){
      if(readdata2$day[i] %in% c("Sat" , "Sun")){
      readdata2$daytype[i] <- "weekend"
    }
  }
  daytype_sum <- readdata2 %>% group_by(daytype , interval) %>% summarize(total_sum = mean(steps))
  
  qplot(interval, total_sum, data= daytype_sum,
      type="l",
      geom="line",
      xlab="Interval",
      ylab="Number of Steps (Average)",
      main="Average steps taken Weekends vs. Weekdays",
      facets =daytype ~ .) 
    
```














